---
title: "figure-7d"
author: "Mac Campbell"
date: "3/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(ape)
library(pegas)
```

##Haplotype network in R

https://johnbhorne.wordpress.com/2016/09/15/still-making-haplotype-networks-the-old-way-how-to-do-it-in-r/

In network-files:     

`./shorten-names-sculpins.pl cytb.fasta  | perl -pe 's/_\d+$|_\d+//g' > haps.fasta`
`mafft haps.fasta > haps.afasta`     

`cat  haps-no-ohlone.afasta  | perl -pe 's/Cottus.pitensis.*/C._pitensis/g' | perl -pe 's/Cottus.gulosus.Kaweah/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.Upper_Kingsgs/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.Lower_Kings/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.Merced/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.Upper_Tuolumne/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.Stanislaus/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.Mokelumne/C._g._gulosus/g' | perl -pe 's/Cottus.gulosus.\w+_American/C._g._wintu/g' | perl -pe 's/Cottus.gulosus.Feather/C._g._wintu/g' | perl -pe 's/Cottus.gulosus.Sac_\w+/C._g._wintu/g' > haps-no-ohlone-renamed.afasta`      

```{r}
Naso<-read.dna(file="network-files/haps-no-ohlone-renamed.afasta", format="fasta")

Naso
```

```{r}
NasoHaps <- haplotype(Naso)
NasoHaps
```


```{r}
NasoNet <- haploNet(NasoHaps)
plot(NasoNet, size=attr(NasoNet,"freq"), fast=FALSE)
#plot(NasoNet, size = attr(NasoNet, “freq”), fast = FALSE)
```

```{r}
ind.hap<-with(
  stack(setNames(attr(NasoHaps, "index"), rownames(NasoHaps))),
  table(hap=ind, individuals=rownames(Naso)[values])
 )
ind.hap
```

```{r}
plot(NasoNet, size=attr(NasoNet, "freq"), scale.ratio = 2, cex = 0.8, pie=ind.hap, labels = FALSE)

legend("topright", c("C. g. gulosus", "C. g. wintu","C. pitensis"), text.col=2:5)
```

     
```{r}
plot(NasoNet, size=attr(NasoNet, "freq"), scale.ratio = 2, cex = 0.8, pie=ind.hap, labels = FALSE, bg = c("#DE9E66","#439AB0","#ACCC66"))
```

     
```{r}
pdf("figure-7/figure-7d.pdf", width=7, height=6)
plot(NasoNet, size=attr(NasoNet, "freq"), scale.ratio = 2, cex = 0.8, pie=ind.hap, labels = FALSE, bg = c("#DE9E66","#439AB0","#ACCC66"))

#legend("topright", c("C. g. gulosus", "C. g. wintu","C. pitensis"), text.col=2:5)
dev.off()
```



     