---
title: "supplementary-figure-s1"
author: "Mac Campbell"
date: "04/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Plots


```{r}
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(grid)
library(gridExtra)
library(viridis)
```

```{r}
cols<-viridis(6, option = "turbo", alpha = 0.75)
#cols<-c("#DE9E66","#439AB0","#E8BEFF","#EEF1A0","#ACCC66")
ggplot()+geom_point(aes(x=c(1,2,3,4,5,6), y=c(1,1,1,1,1,1)), col=cols, cex=5)
ggsave("figure-x/key.jpeg")
```

```{r}
annot<-read_delim("figure-x/pcaScR75.edited.clst", delim="\t", col_names = TRUE)
annot
```
```{r}
levels<-c("COY","GUAD","PEN","UVAS","RUS","RUSEF",
                                            "MER","MOK",
                                            "HSS","McC HB", "SAC",
                                            "PITMC","PITRC",
                                            "McC M", "NAP","WAD","SUS","PUT RR","CLS","PUT BC",
                                            "SAG")
```


Need to generate qopt files.

(base) maccamp@farm:/group/millermrgrp4/maccamp/Sculpin/ADMIX$ gunzip -c admixScR.beagle.gz | wc -l
121816

srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes admixScR.beagle.gz -K 2 -o ngsadmix-k2 -P 12
srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes admixScR.beagle.gz -K 3 -o ngsadmix-k3 -P 12
srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes admixScR.beagle.gz -K 4 -o ngsadmix-k4 -P 12
srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes admixScR.beagle.gz -K 5 -o ngsadmix-k5 -P 12
srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes admixScR.beagle.gz -K 6 -o ngsadmix-k6 -P 12


```{r}
q2<-read_delim("figure-x/ngsadmix-k2.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2) %>%
  rename(Q1=X1, Q2=X2)

df2<-bind_cols(q2, annot)            

df2$Location<-factor(df2$Location, levels=levels)
                     
#levels=c("COY","HSS","GUAD", "McC FR", "McC HB","McC SQ","MER","MOK","PEN",
 #                                           "RUS","RUSEF","SAC","UVAS","PITMC","PITRC","CLS","McC M", "NAP",
  #                                          "PUT BC","PUT RR","SUS","WAD","SAG"))

q2s<-df2 %>% select(Location, IID, Q1, Q2) %>% arrange(Location, IID) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 3:4) %>% mutate(K=2)

pops2<-q2s  %>% group_by(Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Location,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()

```

```{r}
p2 <- ggplot(q2s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops2, x = pops2$Start - 0.5, y=0, xend = pops2$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops2, x = pops2$Stop[length(pops2$Stop)]  + 0.5, y=0, xend= pops2$Stop[length(pops2$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops2$Stop[length(pops2$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  scale_fill_manual(values=c(cols[6], cols[1])) +
  theme(legend.position = "") +
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank()) 
  #scale_x_continuous(breaks=pops2$Position, labels=pops2$Location) 

  
p2

```


```{r}
q3<-read_delim("figure-x/ngsadmix-k3.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2, X3) %>%
  rename(Q1=X1, Q2=X2, Q3=X3)

df3<-bind_cols(q3, annot)            

df3$Location<-factor(df3$Location, levels=levels)
                     
#levels=c("COY","HSS","GUAD", "McC FR", "McC HB","McC SQ","MER","MOK","PEN",
 #                                           "RUS","RUSEF","SAC","UVAS","PITMC","PITRC","CLS","McC M", "NAP",
  #                                          "PUT BC","PUT RR","SUS","WAD","SAG"))

q3s<-df3 %>% select(Location, IID, Q1, Q2, Q3) %>% arrange(Location, IID) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 3:5) %>% mutate(K=3)

pops2<-q3s  %>% group_by(Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Location,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()


p3 <- ggplot(q3s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops2, x = pops2$Start - 0.5, y=0, xend = pops2$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops2, x = pops2$Stop[length(pops2$Stop)]  + 0.5, y=0, 
               xend= pops2$Stop[length(pops2$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops2$Stop[length(pops2$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  scale_fill_manual(values=c(cols[6], cols[1], cols[4])) +
  theme(legend.position = "") +
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank()) 
  #scale_x_continuous(breaks=pops2$Position, labels=pops2$Location) 

  
p3

```

```{r}
q4<-read_delim("figure-x/ngsadmix-k4.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2, X3, X4) %>%
  rename(Q1=X1, Q2=X2, Q3=X3, Q4=X4)

df4<-bind_cols(q4, annot)            

df4$Location<-factor(df3$Location, levels=levels)
                     
#levels=c("COY","HSS","GUAD", "McC FR", "McC HB","McC SQ","MER","MOK","PEN",
 #                                           "RUS","RUSEF","SAC","UVAS","PITMC","PITRC","CLS","McC M", "NAP",
  #                                          "PUT BC","PUT RR","SUS","WAD","SAG"))

q4s<-df4 %>% select(Location, IID, Q1, Q2, Q3, Q4) %>% arrange(Location, IID) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 3:6) %>% mutate(K=3)

pops2<-q4s  %>% group_by(Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Location,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()


p4 <- ggplot(q4s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops2, x = pops2$Start - 0.5, y=0, xend = pops2$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops2, x = pops2$Stop[length(pops2$Stop)]  + 0.5, y=0, 
               xend= pops2$Stop[length(pops2$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops2$Stop[length(pops2$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  scale_fill_manual(values=c(cols[6], cols[4], cols[1], cols[2])) +
  theme(legend.position = "") +
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank()) 
  #scale_x_continuous(breaks=pops2$Position, labels=pops2$Location) 

  
p4

```

```{r}
q5<-read_delim("figure-x/ngsadmix-k5.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2, X3, X4, X5) %>%
  rename(Q1=X1, Q2=X2, Q3=X3, Q4=X4, Q5=X5)

df5<-bind_cols(q5, annot)            

df5$Location<-factor(df3$Location, levels=levels)
                     
#levels=c("COY","HSS","GUAD", "McC FR", "McC HB","McC SQ","MER","MOK","PEN",
 #                                           "RUS","RUSEF","SAC","UVAS","PITMC","PITRC","CLS","McC M", "NAP",
  #                                          "PUT BC","PUT RR","SUS","WAD","SAG"))

q5s<-df5 %>% select(Location, IID, Q1, Q2, Q3, Q4, Q5) %>% arrange(Location, IID) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 3:7) %>% mutate(K=4)

pops2<-q5s  %>% group_by(Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Location,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()


p5 <- ggplot(q5s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops2, x = pops2$Start - 0.5, y=0, xend = pops2$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops2, x = pops2$Stop[length(pops2$Stop)]  + 0.5, y=0, 
               xend= pops2$Stop[length(pops2$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops2$Stop[length(pops2$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  scale_fill_manual(values=c(cols[4], cols[1], cols[6], cols[2], cols[3])) +
  theme(legend.position = "") +
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank()) 
  #scale_x_continuous(breaks=pops2$Position, labels=pops2$Location) 

  
p5

```


```{r}
q6<-read_delim("figure-x/ngsadmix-k6.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2, X3, X4, X5, X6) %>%
  rename(Q1=X1, Q2=X2, Q3=X3, Q4=X4, Q5=X5, Q6=X6)

df6<-bind_cols(q6, annot)            

df6$Location<-factor(df6$Location, levels=levels)
                     
#levels=c("COY","HSS","GUAD", "McC FR", "McC HB","McC SQ","MER","MOK","PEN",
 #                                           "RUS","RUSEF","SAC","UVAS","PITMC","PITRC","CLS","McC M", "NAP",
  #                                          "PUT BC","PUT RR","SUS","WAD","SAG"))

q6s<-df6 %>% select(Location, IID, Q1, Q2, Q3, Q4, Q5, Q6) %>% arrange(Location, IID) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 3:8) %>% mutate(K=6)

pops2<-q6s  %>% group_by(Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Location,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique() %>%
  mutate(Color = ifelse(Location %in% c("PITMC","PITRC"), "#ACCC66", #Pit
                           ifelse(Location %in% c("CLS","McC M","NAP","PUT BC","PUT RR","SUS","WAD"), "grey50",   #Prickly
                           ifelse(Location %in% c("SAG"),"grey50", # Paiute
                           ifelse(Location %in% c("COY","UVAS","PEN","GUAD"),"#E8BEFF", # C o o
                           ifelse(Location %in% c("RUSEF","RUS"), "#EEF1A0", # C o p
                           ifelse(Location %in% c("MER","MOK"), "#DE9E66", # C g g
                           ifelse(Location %in% c("SAC","McC HB","HSS"), "#439AB0", "grey50"))))))))


```

```{r}
p6 <- ggplot(q6s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops2, x = pops2$Start - 0.5, y=0, xend = pops2$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops2, x = pops2$Stop[length(pops2$Stop)]  + 0.5, y=0, xend= pops2$Stop[length(pops2$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+.5, xend= max(pops2$Stop)+.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops2$Stop[length(pops2$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  scale_fill_manual(values=c(cols[5], cols[1], cols[6], cols[2], cols[3], cols[4] )) +
  theme(legend.position = "") +
#  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank()) 
  scale_x_continuous(breaks=pops2$Position, labels=pops2$Location)  +
  theme(axis.text.x = element_text(angle = 45, vjust=0, hjust=.5, color=pops2$Color, face="bold")) 

  
p6

```


```{r}
ggarrange(p2, p3, p4, p5, p6, ncol=1, heights=c(1,1,1,1,1.35))

ggsave("supplemental-figure-s1/supplemental-figure-s1.jpeg", width=9, height=7)
ggsave("supplemental-figure-s1/supplemental-figure-s1.pdf", width=9, height=7)

```
